Pesticides pollution of small streams in Germany

### 2016-07-18 article.tex
setup code / project

Small waterbodies

The aim of this study was 
(i) to compile monitoring data on a national scale and to answer the questions: \\
(ii) Are small agricultural waters more polluted compared to bigger streams? Are there thresholds? \\
(iii)  How polluted are small streams and which pesticides are responsible?

@@

We homogenized and unified these datasets into a common database.
We implemented a robust and transparent data cleaning work flow \citep{poisot_best_2015}, though parts of the dataset are proprietary.
An overview of the data cleaning process is provided in the supplemental materials.

@@

\section{Results}
\subsection{Overview on compiled data}

The compile dataset comprised only a small fraction of stand waters and most of the samples where sampled via grab sampling.
Therefore, we report  only results from streams and grab sampling.
We compiled a national scale dataset  comprising 42236 samples from 3049 sampling sites (Figure \ref{fig:fig1} and Supplement). 
We found big differences in the number of sampling sites between federal states.

>>>>

% Small waterbodies

% runoff during rainfall (Liess et al. 1999)

% underestiamtion of grab sampling (Stehle et al. 2013).

The aim of this study was 
(i) to compile monitoring data on a national scale and to answer the questions: \\
(ii) Is the data a representative description of the pollution situation? \\
(iii) Are small agricultural waters more polluted compared to bigger streams? Are there thresholds? \\
(iv)  How polluted are small streams and which pesticides are responsible?

@@

We homogenized and unified these datasets into a common database.
We implemented a robust and transparent data cleaning work flow \citep{poisot_best_2015}, though parts of the dataset are proprietary.
An overview of the data cleaning process is provided in the supplemental materials.  
The compiled dataset comprised only a small fraction of standing waters and most of the samples where sampled via grab sampling.
Therefore, we report  only results for grab sampling from streams.  \todo{move to results and say that nearly no information on standing waters is available}
To assess whether  grab samples were taken during potential rainfall events we intersected sampling coordinates and date with daily precipitation data \citep{rauthe_central_2013}.

@@

\section{Results}
\subsection{Overview and representativeness of compiled data}

We compiled a national scale dataset  comprising 42236 samples from 3049 sampling sites (Figure \ref{fig:fig1} and Supplement). 
We found big differences in the number of sampling sites between federal states.
